Poseidon Adventure

### 2020-12-07 docs/index.Rmd
update index

### Full age structured data for multispecies modeling, June-October 2020

>>>>

### Full age structured data for multispecies modeling, June-December 2020

<a href="https://sgaichas.github.io/poseidon-dev/SurveyDietCompTest.html" target="_blank">Apply survey specifications to diet outputs, December 7, 2020</a>

<a href="https://sgaichas.github.io/poseidon-dev/msSurveysTest.html" target="_blank">Compare multispecies survey specifications, November 9, 2020</a>
